\chapter{Magnolia 5.0 AdminCentral Module Architecture}
\label{architecture}

The biggest part of the Magnolia 5.0 project is the design and development of
the AdminCentral module - a replacement for the former \emph{AdminInterface}
module. Improved user interface is one of the major targets for AdminCentral
module.

However, the role of AdminCentral is supposed to go far beyond the UI
shell. It is the point of intersection between most of the other modules, a
framework that allows to create complex abstractions on top of their
functionality and provide an easy way to set up communication between them.
In order to fulfill the aforementioned design requirements for extensibility and
mobile platforms support - it was decided to emulate the environment of an
operating system for CMS administration. The resemblence is of course supposed
to be metaphorical, design-wise. The main idea is to have an environment with a
chrome and applications that run inside of it. Such a pattern allows for
creating the additional functionality by merely developing another application.
In order to maintain the common look and feel for all types of platforms the
mobile-like way of UI arrangement was chosen: Single Document Interface (SDI)
with a dashboard and the applications that consume the whole viewport one at a
time.

the AdminCentral is to provide a framework for the applications: both
initial and additional apps must be equally easy to develop, the amount of the
boilerpalte code has to be minimal and the least amount of programming skills
should be required.

The role of \emph{Vaadin} framework in the \emph{AdminCentral} is to make it
possible to achive the compromise between the rich UI and the development
clearness and simplicity.
With Vaadin it is possible to design the entire application development system
completely on the server-side: the user interface can be generated directly form
the configuration templates kept in the storage (JCR) and the powerful
client-server communication mechanism can be used for emulating the navigation
 (based on the browser-fragments).
\input{include/architecture/1-architecture_overview.tex}
\input{include/architecture/2-tech_stack_role_distrib.tex}
\input{include/architecture/3-location_framework.tex}
\input{include/architecture/4-mvp.tex}
\input{include/architecture/5-configuration.tex}
\input{include/architecture/6-shellapps_and_apps.tex}
\input{include/architecture/7-magnolia_shell.tex}
\input{include/architecture/8-actions.tex}

\section{Dependency injection}
\input{include/architecture/di.tex}

\pagebreak